### 2017-02-12 Hhh/Hhh.tex
Committing some updates before edit round 1

Differences in \MET resolution and response between data and \ac{MC} are accounted for by
applying Z--recoil corrections to DY, \Wjets and signal \ac{MC} events. Chapter \ref{chap:objects} 
gives more details on how these corrections are derived.

@@

\section{Background estimation}
\label{sec:hhh_backgrounds}
To estimate the shape and yield of backgrounds in this analysis, data--driven techniques are
used where possible. 
\subsection{\texorpdfstring{\Ztautau}{Z to tau tau}}
\label{sec:hhh_backgrounds_ztt}
The \Ztautau background is estimated using the embedded samples
described in section \ref{sec:hhh_datasets}. To estimate the 
yield of \Ztautau in each category, the total
yield after the initial event selection (before subdividing into categories) as
estimated in \Ztautau \ac{MC} samples is scaled by the efficiency with which 
such events pass the category selection in the embedded sample. The shape of
the \Ztautau background is taken from the embedded sample after applying the full
category selection. The contamination from \ttbar backgrounds in the embedded
sample is accounted for by subtracting this contamination, as evaluated using
the dedicated \ttbar embedded samples, from the \Ztautau background.
\subsection{\texorpdfstring{\ttbar}{ttbar}}
Both the \ttbar shape and normalisation are estimated using \ac{MC} samples.
These are checked against data in dedicated control regions, one such control
region uses the \emu final state of the taus. An \ac{MC}-to-data correction factor is estimated in 
this control region and applied to the yield estimate from \ac{MC} in the signal region. 
\subsection{\texorpdfstring{\Wjets}{W + jets}}
\label{sec:hhh_backgrounds_wjets}
The \Wjets background is greatly reduced by requiring \mT~to
be less than 30 GeV. To estimate the remaining contribution
from \Wjets in the signal region a sideband with \mT~greater
than 70 GeV is used in the 2jet-0tag and 2jet-1tag categories.
Contributions from other backgrounds are subtracted 
from the data in this region, and a high-\mT~to low- \mT~
extrapolation factor is determined from the \Wjets \ac{MC} 
samples. The yield in the signal region is given by the data yield in the high-\mT sideband, with
other backgrounds subtracted, multiplied by this extrapolation factor.
In the 2jet-2tag category, a slightly different high-\mT~sideband of 60-120 GeV is used 
to give more events for the \Wjets estimate after other backgrounds are
subtracted. The method of extrapolating this yied estimate into
the signal region is otherwise analogous.

>>>>

Differences in \MET resolution and response between data and \ac{MC} are accounted for by
applying Z--recoil corrections to DY, \Wjets and signal \ac{MC} events. Section \ref{sec:objects_met_recoilcorr} 
gives more details on how these corrections are derived.

@@

\section{Background estimation}
\label{sec:hhh_backgrounds}
To estimate the shape and yield of backgrounds in this analysis, data--driven techniques are
used where possible. 
\subsection{\texorpdfstring{\Ztautau}{Z to tau tau}}
\label{sec:hhh_backgrounds_ztt}
The \Ztautau background is estimated using the embedded samples
described in section \ref{sec:hhh_datasets}. To estimate the 
yield of \Ztautau in each category, the total
yield after the initial event selection (before subdividing into categories) as
estimated in \Ztautau \ac{MC} samples is scaled by the efficiency with which 
such events pass the category selection in the embedded sample. The shape of
the \Ztautau background is taken from the embedded sample after applying the full
category selection. The contamination from \ttbar backgrounds in the embedded
sample is accounted for by subtracting this contamination, as evaluated using
the dedicated \ttbar embedded samples, from the \Ztautau background.
\subsection{\texorpdfstring{\ttbar}{ttbar}}
Both the \ttbar shape and normalisation are estimated using \ac{MC} samples.
These are checked against data in dedicated control regions, one such control
region uses the \emu final state of the taus. An \ac{MC}-to-data correction factor is estimated in 
this control region and applied to the yield estimate from \ac{MC} in the signal region. 
\subsection{\texorpdfstring{\Wjets}{W + jets}}
\label{sec:hhh_backgrounds_wjets}
The \Wjets background is greatly reduced by requiring \mT~to
be less than 30 GeV. To estimate the remaining contribution
from \Wjets in the signal region a sideband with \mT~greater
than 70 GeV is used in the 2jet-0tag and 2jet-1tag categories.
Contributions from other backgrounds are subtracted 
from the data in this region, and a high-\mT~to low- \mT~
extrapolation factor is determined from the \Wjets \ac{MC} 
samples. The yield in the signal region is given by the data yield in the high-\mT~sideband, with
other backgrounds subtracted, multiplied by this extrapolation factor.
In the 2jet-2tag category, a slightly different high-\mT~sideband of 60-120 GeV is used 
to give more events for the \Wjets estimate after other backgrounds are
subtracted. The method of extrapolating this yied estimate into
the signal region is otherwise analogous.
